---
title: "Assignment 1"
subtitle: "612203012"
output:
  pdf_document: default
  html_notebook: default
header-includes:
  \usepackage{fvextra}
  \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---
\fontfamily{cmr}
\fontsize{13}{23}
\fontseries{b}
\selectfont

\

# Q1
Install given packages

```{r}
install.packages(c('plyr', 'MASS', 'ggplot2', 'dplyr'), repos = "https://cran.icts.res.in/")
```

\newpage

# Q2
Find answers to log2(2*\*5) and log(exp(1)*exp(1))

```{r}
log2(2^5)
log(exp(1)*exp(1))
```

\newpage

# Q3
Implement functions using built-in dataset

```{r}
data(iris) #loading the dataset
iris
summary(iris)
class(iris)
typeof(iris)
head(iris)
tail(iris)
str(iris)
species_habitat = data.frame(Species = c("setosa", "versicolor", "virginica"), Habitat = c("Woodland", "Meadow", "Mountain"))
species_habitat
merged_dataset = merge(iris, species_habitat, by = "Species")
merged_dataset
```

\newpage

# Q4
Create a two-dimensional 5×3 array of sequence of even integers > 50

```{r}
v = seq(52, 80, 2)
a = array(v, dim = c(5,3))
a
```
\

# Q5
Create a vector which contains 10 integer values between -50 and +50


```{r}
vec = seq(-45, 45, 10)
vec
```

\newpage

# Q6
Suppose age is a vector containing ages of 10 persons. Solve the given questions.

```{r}
#(a) Access the age of fourth person
age = c(22, 27, 31, 41, 30, 25, 19, 20, 23, 35)
age
age[4] 

#(b) Vector with age>30
age30 = age[age > 30] 
age30

#(c) Ages of last 3 persons
age[8:10] 

#(d) No of elements in vector age
length(age)

#(e) Ages of persons except 5th and 7th
age[c(-5, -7)]

#(f) Vector with ages between 20 and 25
age2 = age[age > 20 & age < 25]
age2
```
\

# Q7
Create factor from given data and find levels

```{r}
f = factor(c(1,2,3,2,3,1,4,2,3,NA,5,3,2))
f
levels(f)
```

\newpage

# Q8
List containing strings, numbers, vectors and logical values

```{r}
l = list(15L, 2.5, 9.3, 10L, "probability", FALSE, "Statistics", c(1,2,3), seq(1, 10, 3), TRUE)
l
```
\

# Q9
Using built-in dataset iris, find out categorical variables

```{r}
library(dplyr)
names(select_if(iris, is.factor))
```

\

# Q10
Create a numeric vector c(1:5) and a 5 by 3 matrix with elements from 1 to 15

```{r}
n = c(1:5)
n
```

\

# Q11
Create a dataframe of the given dataset and solve the questions

```{r}
df = data.frame(height = c(140,137,150,147,139,140,150,132,138,140), weight = c(55,57,59,62,61,60,60,58,59,57))
df #Required dataframe

#(a) Vector h1 with height > 145 cm
h1 = df$height[df$height>145]
h1

#(b) Vector h2 with weight > 55 kg
h2 = df$height[df$weight>55]
h2

#(c) Vector h3 with height > 140 and weight > 60
h3 = df$height[df$height>140 & df$weight>60]
h3
```